---
title: "Fitting epicurves"
author: "Tim Taylor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fitting epicurves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.width = 7,
  fig.height = 5
)
```

# Example
To illustrate the trend fitting functionality of *incidence2plus* we will use
the simulated Ebola Virus Disease (EVD) outbreak data from the
[outbreaks](https://CRAN.R-project.org/package=outbreaks) package.

## Loading relevant packages and data
```{r}
library(outbreaks)
library(incidence2)
library(incidence2plus)
library(tidyr)

raw_dat <- ebola_sim_clean$linelist
```

For this example we will restrict ourselves to the first 20 weeks of data:

```{r}
dat <- incidence(
    raw_dat, 
    date_index = date_of_onset,
    interval = 7
)[1:20, ]
dat
plot(dat)
```

## Modeling incidence
We can use `fit_curve()` to fit the data with either a poisson or 
negative binomial regression model.  The output from this will be a nested
object with class [incidence2_fit] which as methods available for both 
automatic plotting and the calculation of growth (decay) rates and doubling
(halving) times.

```{r}
out <- fit_curve(dat, model = "poisson", alpha = 0.05)
out
out %>% unnest(estimates)
out %>% plot()
out %>% growth_rate()
```

`fit_curve` will also work on grouped incidence objects:

```{r}
grouped_dat <- incidence(
    raw_dat, 
    date_index = date_of_onset,
    interval = 7,
    groups = hospital
)[1:140, ]
grouped_dat

out <- fit_curve(grouped_dat, model = "poisson", alpha = 0.05)
out
out %>% plot()
out %>% growth_rate()
```

## Rolling average
We can add a rolling average, across current and previous intervals, to
an `incidence2` object with the `add_rolling_average()` function:

```{r rolling_average}
ra <- 
  grouped_dat %>% 
  add_rolling_average(before = 2) # group observations with the 2 prior
ra
ra %>% unnest(rolling_average)

plot(ra, color = "white")
```